---
title: "Condition Index of Natural vs. Restored Oysters"
output: html_notebook
---

This analysis will focus on Ninigret Pond, because we have the presence of natural reefs, restored reefs, and aquaculture in order to make direct comparisons.

In Ninigret, we have 3 treatments for oysters:

* Aquaculture
* Natural (Foster Cove)
* Restored (FHE)

# Compare Condition Indices:
<br>
## Number of replicates per treatment
```{r echo = TRUE}
# Load necessary packages
library("plyr") #loads count()

# Read data into R
oyster_dat <- read.csv("oyster_data.csv")

# Subset only oysters collected in Ninigret/Foster Cove
ninigret_dat <- subset(oyster_dat, oyster_dat$Site == c("Ninigret FHE","Foster Cove"))

# Remove all oysters not measured for condition
CI_dat <- subset(ninigret_dat, ninigret_dat$Total_Mass_g != "")
CI_dat$Total_Mass_g <- as.numeric(CI_dat$Total_Mass_g )
CI_counts <- count(CI_dat$Site)
colnames(CI_counts) <- c("Treatment","Replicates")
CI_counts

# Remove unnecessary columns
CI_dat <- CI_dat[,-c(7:10)]

```
<br>
<br>
The sample sizes are not equal, but they are very close.
<br>
<br>

## Calculate Condition Index 

Condition Index is a common way to assess the effects of environmental conditions, such as salinity, temperature, tidal elevation, food quality, pollution, and presence of parasites, on oysters is by comparing condition index (CI) values among oysters exposed to differing conditions or located in various locations (e.g. Lawrence and Scott 1982, Rainer and Mann 1992, Rheault and Rice 1996).
<br>
<br>
Formula for calculating CI:
<br>
CI = (Tissue Dry Weight * 100)/(Shell Dry Weight)
<br>
<br>
```{r}
# Calculate CI for oysters
CI_dat$CI <- (CI_dat$Total_Dry_Tissue_g * 100)/(CI_dat$Total_Dry_Shell_g)

```

## Plot linear relationship of Dry Tissue / Dry Shell

```{r}
all_reg <- lm(CI_dat$Total_Dry_Tissue_g ~ CI_dat$Total_Dry_Shell_g)
print(summary(all_reg))
plot(CI_dat$Total_Dry_Tissue_g ~ CI_dat$Total_Dry_Shell_g,
     xlab = "Dry Shell Weight (g)", ylab = "Dry Tissue Weight (g)",
     pch = 16)
abline(all_reg)
```
Adjusted R-squared:  0.8804

Some outliers are present.

## Plot linear relationship by Pond

```{r echo = FALSE}
FHE_reg <- lm(CI_dat$Total_Dry_Tissue_g[CI_dat$Culture == "FHE"] ~
                                           CI_dat$Total_Dry_Shell_g[CI_dat$Culture == "FHE"])
nat_reg <- lm(CI_dat$Total_Dry_Tissue_g[CI_dat$Culture == "Natural"] ~
                                           CI_dat$Total_Dry_Shell_g[CI_dat$Culture == "Natural"])
plot(CI_dat$Total_Dry_Tissue_g ~ CI_dat$Total_Dry_Shell_g,
     xlab = "Dry Shell Weight (g)", ylab = "Dry Tissue Weight (g)",
     pch = 16)
points(CI_dat$Total_Dry_Shell_g[CI_dat$Culture == 'FHE'], 
        CI_dat$Total_Dry_Tissue_g[CI_dat$Culture == 'FHE'], 
       pch=16, col='red')
points(CI_dat$Total_Dry_Shell_g[CI_dat$Culture == 'Natural'], 
        CI_dat$Total_Dry_Tissue_g[CI_dat$Culture == 'Natural'], 
       pch=16, col='green')
legend('bottomright',legend = unique(CI_dat$Culture), pch = 16, bty = 'o', 
       col = c('red','green'))
abline(FHE_reg, col = "red")
abline(nat_reg, col = "green")
```

## Plot variance across length

This plot looks funny, will troubleshoot.

```{r}
FHE_CI_reg <- lm(CI_dat$CI[CI_dat$Culture == "FHE"] ~
                                           CI_dat$Total_Dry_Shell_g[CI_dat$Culture == "FHE"])
nat_CI_reg <- lm(CI_dat$CI[CI_dat$Culture == "Natural"] ~
                                           CI_dat$Total_Dry_Shell_g[CI_dat$Culture == "Natural"])
plot(CI_dat$CI ~ CI_dat$Total_Dry_Shell_g,
     xlab = "Dry Shell Weight (g)", ylab = "Condition Index",
     pch = 16)
points(CI_dat$CI[CI_dat$Culture == 'FHE'], 
        CI_dat$Total_Dry_Tissue_g[CI_dat$Culture == 'FHE'], 
       pch=16, col='red')
points(CI_dat$CI[CI_dat$Culture == 'Natural'], 
        CI_dat$Total_Dry_Tissue_g[CI_dat$Culture == 'Natural'], 
       pch=16, col='green')
legend('bottomright',legend = unique(CI_dat$Culture), pch = 16, bty = 'o', 
       col = c('red','green'))
abline(FHE_CI_reg, col = "red")
abline(nat_CI_reg, col = "green")
```



```{r}
library(car)




CI_dat$Site <- factor(CI_dat$Site)
boxplot(CI_dat$CI ~ CI_dat$Site)

CI_aov <- lm(CI ~ Site + Total_Dry_Shell_g, CI_dat)

leveneTest(lm(CI ~ Site, CI_dat))
shapiro.test(CI_aov$residuals)


anova(lm(CI ~ Site + Total_Dry_Shell_g, CI_dat))
```

Data are normally distributed, but have unequal variances.  Will perform Welch's ANOVA

## Statistical Analysis

```{r}
oneway.test(CI ~ Site, CI_dat, var.equal = FALSE)
```


## Final Plot

```{r}
library(sciplot)

CI_plot_mean <- aggregate(CI_dat$CI~CI_dat$Site, FUN = mean)
colnames(CI_plot_mean) <- c("Treatment","Mean")
CI_plot_se<- aggregate(CI_dat$CI~CI_dat$Site, FUN = se)
colnames(CI_plot_se) <- c("Treatment", "SE")

CI_plot_dat <- merge(CI_plot_mean, CI_plot_se, by = "Treatment")

CI_plot <- ggplot(CI_plot_dat, aes(x=Treatment, y=Mean)) + 
  geom_bar(position=position_dodge(), stat="identity",colour = "black", fill = "grey") +
  geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE),
                width=.4,                    # Width of the error bars
                position=position_dodge(.9)) +
  ylab("Mean Condition Index") + 
  xlab("Treatment") + 
  theme(axis.text = element_text(size = 12),legend.title=element_text(size=12),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = ("black"))) + 
        scale_y_continuous(expand = c(0, 0), limits = c(0,5))
CI_plot
```

### N for each treatment

```{r}
count(CI_dat, vars = "Culture")
```

